Equalizer: A Mature Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Missing CGLX ref
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@20 db7c848b-7755-4df2-b763-8796797afa52

The concept of transparent OpenGL interception popularized by WireGL and
Chromium~\cite{HHNFAKK:02} has received little attention since 2009. While some
commercial implementations such as TechViz and MechDyne Conduit continue to
exist, on the research side only ClusterGL~\cite{NHM:11} has been
presented. ClusterGL employs the same approach as Chromium, but delivers a
significantly faster implementation of transparent OpenGL interception and
distribution for parallel rendering. CGLX~\cite{CGLX:11} tries to bring parallel
execution transparently to OpenGL applications, by emulating the GLUT API and
intercepting certain OpenGL calls. This approach works transparently for trivial
applications, but quickly requires the application developer to address the
complexities of a distributed application when mutable application state needs
to be synchronized across processes.

@@

\cite{DK:11}: Framework to develop apps for multitile, thus targeted
specifically for tiled-wall visualization systems: grid configuration,
scalability (?), multiple work sessions, multiuser events. Master-slave approach
like Eq. with grid nodes running instances of the application. Is maybe more
like a GLUT and window replacement, or enhancement to deal with the OpenGL
contexts and events

>>>>

The concept of transparent OpenGL interception popularized by WireGL and
Chromium~\cite{HHNFAKK:02} has received little attention since 2009. While some
commercial implementations such as TechViz and MechDyne Conduit continue to
exist, on the research side only ClusterGL~\cite{NHM:11} has been
presented. ClusterGL employs the same approach as Chromium, but delivers a
significantly faster implementation of transparent OpenGL interception and
distribution for parallel rendering. CGLX~\cite{DK:11} tries to bring parallel
execution transparently to OpenGL applications, by emulating the GLUT API and
intercepting certain OpenGL calls. This approach works transparently for trivial
applications, but quickly requires the application developer to address the
complexities of a distributed application when mutable application state needs
to be synchronized across processes.

@@
